Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-26 analysis/paper/paper.qmd
added shapefile
Added shapefile data
stash
exploring GIS files

# korean_archaeological_site_locations_tcsa <- 
#   tcsa_site_ass %>% 
#   mutate(Site_name = str_remove(Assemblage, "_.*")) %>%  
#   full_join(korean_archaeological_site_locations) %>% 
#   drop_na(min_tcsa)

korean_archaeological_site_locations_tcsa <- tcsa %>% 
  full_join(korean_archaeological_site_locations) %>% 
  drop_na(min_tcsa)

@@

>>>>

korean_archaeological_site_locations_tcsa <- 
  tcsa %>% 
  mutate(Site_name_to_join = str_squish(Site_name)) %>% 
  left_join(korean_archaeological_site_locations %>% 
              mutate(Site_name_to_join  = str_squish(Site_name)),
                     by = "Site_name_to_join") %>% 
  drop_na(min_tcsa)

@@

library(sf)

veg <- read_sf(here("analysis/data/gis_data/vegetation_polygons.shp"))

# take a look
ggplot() +
  geom_sf(data = veg)

# BM: basic plan is the do a spatial join with the veg zones and the TCSA values. Then table of artefacts will get a new column telling us what veg zone it is in. Then we can make a plot to compare the distribution of tcsa values across the different veg zones

# Determine which points fall inside which polygons

# Convert to class 'sf'
pts <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c( "long_dd", "lat_dd"),
                crs = st_crs(4326))

# take a look
ggplot() +
  geom_sf(data = pts)

points_in_veg_zones <- 
st_join(pts, 
        veg, 
        join = st_contains)
